### 2017-09-01 paper/evaluation.tex
dir rename
Pass on text

From these \SubjectsGithub{} downloaded projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory and \SubjectsGithubNotTestable{}
projects were unable to test due to incompatible environment (\eg,
missing required web browser or database management system).
In addition, we identified \SubjectsGithubFlaky{} projects with
non-deterministic test results.
In general, a test that either pass or fail under the same circumstances
is known as a ``flaky test''~\cite{luo-etal-fse2014}.
\Comment{While there are several causes that may introduce randomness on test
results, our concern is on flakiness caused by
parallel execution.}
As some of our experiments consist in running tests on different
threads, we ignored these projects as it would be impractical
to identify whether a test failed due to a race condition or some
other source of flakiness.
Our final set of subjects consists of \numSubjs{} projects.
Figure~\ref{fig:subjects} summarizes our sample set.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
  \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
  hosted on \github{}. From this initial sample, we ignored
  \SubjectsGithubNotMaven{} projects without Maven support,
  \SubjectsGithubNotTestable{} projects unable to test, and
  \SubjectsGithubFlaky{} projects with flaky tests. We considered
  \numSubjs{} projects to conduct our study.}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}{0.182\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/barplot-timecost.pdf}
        \caption{\label{fig:rq1-barplot}}
    \end{subfigure}%
    ~
    \begin{subfigure}{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/boxplot-timecost.pdf}
        \caption{\label{fig:rq1-boxplot}}
    \end{subfigure}%
    \caption{(a) Subjects grouped by time cost ($t$): short run ($t <
    1m$), medium run ($1m \le t < 5m$), and long run ($5m \le t$); (b)
    Distribution of time cost by group.}
\end{figure}

@@

It is important to note that we under-estimated cost in our
experiments for two main reasons.  First, some tests may finish
earlier than expected due to the observed test failures in some of the
revisions we downloaded. From the \numSubjs{} testable projects,
\numSubjsPass{} successfully executed all tests and \numSubjsFail{}
reported some test failures.
\Jbc{
From these \numSubjsFail{} subjects, 67 projects have less than 10\%
of failing tests.
}
Second, some projects may omit long-running tests on their default
execution. For instance, the project \CodeIn{apache.maven-surefire}
runs all unit tests in a few seconds.  According to our criteria, this
project is to be classified as \shortg{} but a closer look reveals
that only smoke tests are run by default in this project.
Time-consuming integration and system tests are only accessible via
custom parameters, which we do not handle in our experimental setup.
We enabled such parameters for this specific project and observed that
testing time goes to nearly 30 minutes.  For simplicity, we considered
only the tests executed by default.

\vspace{1ex}
\begin{center}
\fbox{
\begin{minipage}{8cm}
    \textit{Answering \numRQFeasibilityOne{}:}~\emph{We conclude that
      time-consuming test suites are relatively frequent in
      open-source projects.  We found that \percentMedLongRunning{} of
      the \numSubjs{} projects we analyzed (\ie{}, over 1 in every 6
      projects) take at least 1 minute to run and
      \percentLongRunning{} take at least 5 minutes to run.\Comment{
        (\ie, \numMedLong{} projects from \medg{} and \longg{}).}}
\end{minipage}
}
\end{center}
\vspace{1ex}

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group.}
    \end{subfigure}
    %% \vspace{2ex}
    %% \begin{subfigure}{0.5\textwidth}
    %%   \centering
    %%   \begin{tabular}{rrrr}
    %%     \toprule
    %%     & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
    %%     \midrule    
    %%     Long   &  7 & 15 & 12 \\
    %%     Medium & 22 & 19 & 7 \\
    %%     \bottomrule
    %%   \end{tabular}
    %%   \caption{\label{fig:sd}Standard deviation ($\sigma$) of test case running times.}
    %% \end{subfigure}
    \caption{\label{fig:time-distributions}Time distributions. X-axis
        denote projects appearing in arbitrary order.}%
\end{figure}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.15\textwidth}
    \centering
    \includegraphics[width=.85\textwidth]{plots/boxplots-testcases.pdf}
    \caption{\label{fig:size-testsuites}Size of test suites.}
  \end{subfigure}
  ~
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=.95\textwidth]{plots/scatter-testcost.pdf}
    \caption{\label{fig:scattercost}Size versus running time of
      test suites.}
  \end{subfigure}
  \caption{\label{fig:time-versus-size}Relating size and time.}%
\end{figure}

@@

It came as a surprise the observation that
no project used distinct configurations in their modules. Considering
our set of \numMedLong{} projects, we found that only
\textbf{\numProjectsPar{}} of those projects had parallelism enabled
by default, with only configurations \ParClassSeqMeth{},
\ParClassParMeth{}, and \ForkSeq{} being used.  Configurations
\ParClassParMeth{} and \ForkSeq{} were the most popular among these
cases.  Note that these results under-approximate real usage of
parallelism as we used default parameters in our scripts to spawn the
Maven process.  That decision could prevent execution of particular
test modules.
%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}

@@

%% \begin{figure}[ht!]
%%     \centering
%%     \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccc}
%%         \toprule
%%         \multirow{2}{*}{Group} %1st row, 1st cell
%%             & \multirow{2}{*}{\# \pomf{}}
%% 	    & \# \pomf{} matched\\
%%         % 2nd row - empty cell
%%             & % empty cell
%%             & / total\\%
%%         \midrule%
%% 	Long   & \numPomLong{} & 4 / \numLong{}\\%
%% 	Medium & \numPomMed{} & 6 / \numMed{}\\%
%%         \midrule%
%%         Total % last row, first cell
%%             & \pomMedLong{}
%%             & \numProjectsPar{} / \numMedLong{}\\%
%%         \bottomrule%
%%     \end{tabular*}
%%     \caption{Presence of parallelization settings in build files: the
%%     first column indicates the group of projects according to their
%%     time cost; the second column is the subset of files with parallelization
%%     keywords; the last column indicates the ratio of projects with
%%     parallelism support.}
%%     \label{tab:inspection-table} 
%% \end{figure}
%% \Jbc{rework this... $\rightarrow$} From the \numProjectsPar{} projects
%% identified above, we investigated further the \numPomMatched{}
%% build files with parallel settings.  We analyzed the support and
%% distribution of parallel modes from this subset of projects. To
%% calculate the distribution of parallel modes, we considered only the
%% presence of the mode in at least one of the project settings.  Recall
%% that a build file may contain more than one parallel setting and a
%% project may contain several sub-modules with build files.  In case the
%% value of a parallel option is resolved dynamically (\eg, via
%% command-line argument or system variable) we compute all modes related
%% to the option. For instance, depending on the value, the
%% \CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
%% \ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
%% (\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
%% Figure~\Fix{fig:freqmodes-static} summarizes our findings.
%% \Fix{Missing conclusion: Fork the most used configuration}
%% \begin{figure}[h!]
%%     \centering
%%     \includegraphics[width=0.32\textwidth]{plots/barplot-modes-static.pdf}
%% 	\caption{\label{fig:freqmodes-static}\Luis{This is wrong, it
%% 	should be \textbf{CF0} instead of \textbf{CL0}}Distribution of parallel modes
%%     identified statically in a subset of \numProjectsPar{} projects.
%%     A project may have support to more than one parallel mode.}
%% \end{figure}

@@

Considering question 3, the distribution of answers was as follows.  A
total of \emailsA{} of the \emailsProjectsAnswered{} developers who
answered the survey did not know that parallelism was available in
Maven (option ``a''), \emailsB{} of developers mentioned that they did
not use parallelism concerned with possible concurrency issues (option
``b''), \emailsD{} of developers mentioned that continuous integration
services sufficed to provide timely feedback while running only smoke
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.18\textwidth]{plots/survey.pdf}
    \caption{\label{fig:rq5-answers}Summary of developer's answers to
      survey question~\ref{questionThree}.}
\end{wrapfigure}
tests (\ie{}, short-running tests) locally (option ``c'')\Comment{here
  I want to say that they use it for something like "non-blocking
  testing" while developing in a local machine}, and \emailsD{} of
developers who provided an alternative answer (option ``d'') mentioned
that using parallelism was not worth the effort of preparing the test
suites to take advantage of available processing power.  A total of
\emailsNA{} of participants did not answer the last question of the
survey.  The pie chart in Figure~\ref{fig:rq5-answers} 
summarizes the distribution of answers.

>>>>

From these \SubjectsGithub{} downloaded projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory and \SubjectsGithubNotTestable{}
projects were unable to test due to incompatible environment (\eg,
missing required web browser or database management system).
In addition, we identified \SubjectsGithubFlaky{} projects with
non-deterministic test results.
In general, a test that either pass or fail under the same circumstances
is known as a ``flaky test''~\cite{luo-etal-fse2014}.
\Comment{While there are several causes that may introduce randomness on test
results, our concern is on flakiness caused by
parallel execution.}
As some of our experiments consist in running tests on different
threads, we ignored these projects as it would be impractical
to identify whether a test failed due to a race condition or some
other source of flakiness.
\Jbc{From the \SubjectsGithubConsistant{} projects with
deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
projects with more than \SuiteFailingThreshold{} of tests failing to
reduce bias in our dataset.}
Our final set of subjects consists of \numSubjs{} projects.
Figure~\ref{fig:subjects} summarizes our sample set.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.25\textwidth]{results/piechart-subjs.pdf}
  \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
  hosted on \github{}. From this initial sample, we ignored
  \SubjectsGithubNotMaven{} projects without Maven support,
  \SubjectsGithubNotTestable{} projects unable to test,
  \SubjectsGithubFlaky{} projects with flaky tests, and
  \SubjectsGithubTooManyFailures{} projects had at least
  \SuiteFailingThreshold{} of failing tests. We considered
  \numSubjs{} projects to conduct our study.}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}{0.182\textwidth}
        \centering
        \includegraphics[width=\textwidth]{results/barplot-timecost.pdf}
        \caption{\label{fig:rq1-barplot}}
    \end{subfigure}%
    ~
    \begin{subfigure}{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{results/boxplot-timecost.pdf}
        \caption{\label{fig:rq1-boxplot}}
    \end{subfigure}%
    \caption{(a) Subjects grouped by time cost ($t$): short run ($t <
    1m$), medium run ($1m \le t < 5m$), and long run ($5m \le t$); (b)
    Distribution of time cost by group.}
\end{figure}

@@

It is important to note that we under-estimated cost in our
experiments for one main reason.
Some projects may omit long-running tests on their default
execution. For instance, the project \CodeIn{apache.maven-surefire}
runs all unit tests in a few seconds.  According to our criteria, this
project is to be classified as \shortg{} but a closer look reveals
that only smoke tests are run by default in this project.
Time-consuming integration and system tests are only accessible via
custom parameters, which we do not handle in our experimental setup.
We enabled such parameters for this specific project and observed that
testing time goes to nearly 30 minutes.  For simplicity, we considered
only the tests executed by default.
\Jbc{
Although failing tests may introduce noise in our measurements, we
carefully eliminated subjects with more than \SuiteFailingThreshold{} of
test failures. 
From the \numSubjs{} testable projects, \numSubjsPass{} successfully
executed all tests and \numSubjsFail{} reported some test failure.
Furthermore, from these \numSubjsFail{} subjects, only 11 subjects
have more than 5\% of failing tests (7.3\% in average).
}
\vspace{1ex}
\begin{center}
\fbox{
\begin{minipage}{8cm}
    \textit{Answering \numRQFeasibilityOne{}:}~\emph{We conclude that
      time-consuming test suites are relatively frequent in
      open-source projects.  We found that \percentMedLongRunning{} of
      the \numSubjs{} projects we analyzed (\ie{}, over 1 in every 5
      projects) take at least 1 minute to run and
      \percentLongRunning{} take at least 5 minutes to run.\Comment{
        (\ie, \numMedLong{} projects from \medg{} and \longg{}).}}
\end{minipage}
}
\end{center}
\vspace{1ex}

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{results/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{results/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group.}
    \end{subfigure}
    %% \vspace{2ex}
    %% \begin{subfigure}{0.5\textwidth}
    %%   \centering
    %%   \begin{tabular}{rrrr}
    %%     \toprule
    %%     & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
    %%     \midrule    
    %%     Long   &  7 & 15 & 12 \\
    %%     Medium & 22 & 19 & 7 \\
    %%     \bottomrule
    %%   \end{tabular}
    %%   \caption{\label{fig:sd}Standard deviation ($\sigma$) of test case running times.}
    %% \end{subfigure}
    \caption{\label{fig:time-distributions}Time distributions. X-axis
        denote projects appearing in arbitrary order.}%
\end{figure}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.15\textwidth}
    \centering
    \includegraphics[width=.85\textwidth]{results/boxplots-testcases.pdf}
    \caption{\label{fig:size-testsuites}Size of test suites.}
  \end{subfigure}
  ~
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=.95\textwidth]{results/scatter-testcost.pdf}
    \caption{\label{fig:scattercost}Size versus running time of
      test suites.}
  \end{subfigure}
  \caption{\label{fig:time-versus-size}Relating size and time.}%
\end{figure}

@@

It came as a surprise the observation that
no project used distinct configurations in their modules. Considering
our set of \numMedLong{} projects, we found that only
\textbf{\numProjectsPar{}} of those projects had parallelism enabled
by default, with only configurations \ParClassSeqMeth{},
\ParClassParMeth{}, and \ForkSeq{} being used.  Configurations
\ParClassParMeth{} and \ForkSeq{} were the most popular among these
cases.  Note that these results under-approximate real usage of
parallelism as we used default parameters in our scripts to spawn the
Maven process.  That decision could prevent execution of particular
test modules.
%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{results/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}

@@

%% \begin{figure}[ht!]
%%     \centering
%%     \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccc}
%%         \toprule
%%         \multirow{2}{*}{Group} %1st row, 1st cell
%%             & \multirow{2}{*}{\# \pomf{}}
%% 	    & \# \pomf{} matched\\
%%         % 2nd row - empty cell
%%             & % empty cell
%%             & / total\\%
%%         \midrule%
%% 	Long   & \numPomLong{} & 4 / \numLong{}\\%
%% 	Medium & \numPomMed{} & 6 / \numMed{}\\%
%%         \midrule%
%%         Total % last row, first cell
%%             & \pomMedLong{}
%%             & \numProjectsPar{} / \numMedLong{}\\%
%%         \bottomrule%
%%     \end{tabular*}
%%     \caption{Presence of parallelization settings in build files: the
%%     first column indicates the group of projects according to their
%%     time cost; the second column is the subset of files with parallelization
%%     keywords; the last column indicates the ratio of projects with
%%     parallelism support.}
%%     \label{tab:inspection-table} 
%% \end{figure}
%% \Jbc{rework this... $\rightarrow$} From the \numProjectsPar{} projects
%% identified above, we investigated further the \numPomMatched{}
%% build files with parallel settings.  We analyzed the support and
%% distribution of parallel modes from this subset of projects. To
%% calculate the distribution of parallel modes, we considered only the
%% presence of the mode in at least one of the project settings.  Recall
%% that a build file may contain more than one parallel setting and a
%% project may contain several sub-modules with build files.  In case the
%% value of a parallel option is resolved dynamically (\eg, via
%% command-line argument or system variable) we compute all modes related
%% to the option. For instance, depending on the value, the
%% \CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
%% \ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
%% (\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
%% Figure~\Fix{fig:freqmodes-static} summarizes our findings.
%% \Fix{Missing conclusion: Fork the most used configuration}
%% \begin{figure}[h!]
%%     \centering
%%     \includegraphics[width=0.32\textwidth]{results/barplot-modes-static.pdf}
%% 	\caption{\label{fig:freqmodes-static}\Luis{This is wrong, it
%% 	should be \textbf{CF0} instead of \textbf{CL0}}Distribution of parallel modes
%%     identified statically in a subset of \numProjectsPar{} projects.
%%     A project may have support to more than one parallel mode.}
%% \end{figure}

@@

Considering question 3, the distribution of answers was as follows.  A
total of \emailsA{} of the \emailsProjectsAnswered{} developers who
answered the survey did not know that parallelism was available in
Maven (option ``a''), \emailsB{} of developers mentioned that they did
not use parallelism concerned with possible concurrency issues (option
``b''), \emailsD{} of developers mentioned that continuous integration
services sufficed to provide timely feedback while running only smoke
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.18\textwidth]{results/survey.pdf}
    \caption{\label{fig:rq5-answers}Summary of developer's answers to
      survey question~\ref{questionThree}.}
\end{wrapfigure}
tests (\ie{}, short-running tests) locally (option ``c'')\Comment{here
  I want to say that they use it for something like "non-blocking
  testing" while developing in a local machine}, and \emailsD{} of
developers who provided an alternative answer (option ``d'') mentioned
that using parallelism was not worth the effort of preparing the test
suites to take advantage of available processing power.  A total of
\emailsNA{} of participants did not answer the last question of the
survey.  The pie chart in Figure~\ref{fig:rq5-answers} 
summarizes the distribution of answers.

### 2017-09-01 paper/threats.tex
Pass on text

The main threats to validity of this study are the following.
\textit{External Validity:} Generalization of our findings is limited
to our selection of subjects, testing framework, and build system.  To
mitigate that issue, we selected subjects according to an objective
criteria, described in Section~\ref{sec:subjects}.  It remains to
evaluate the extent to which our observations would change when using
different testing frameworks and build systems.
\textit{Internal Validity:} Our results could be influenced by
unintentional mistakes made by humans who interpreted survey data and
implemented scripts and code to collect and analyze data.
For example, we developed JUnit runners to reproduce Maven's parallel
configurations and implemented several scripts to automate our
experiments (\eg, run tests and detect parallelism enabled by default
in the subjects).
All those tasks could introduce bias in our results.
To mitigate those threats, we worked in pairs as to increase chances
of capturing unintentional mistakes.
\textit{Construct Validity:} We considered a number of metrics in this
study that could influence some of our interpretations.  For example,
we measured number of test cases per suite, distribution of test costs
in a suite, time to run a suite, etc.  In principle, these metrics may
not reflect the main problems associated with test
efficiency.

>>>>

The main threats to validity of this study are the following.
\textit{External Validity:} Generalization of our findings is limited
to our selection of subjects, testing framework, and build system.  To
mitigate that issue, we selected subjects according to an objective
criteria, described in Section~\ref{sec:subjects}.  It remains to
evaluate the extent to which our observations would change when using
different testing frameworks and build systems.
\Jbc{Also, some of the selected subjects contain failing tests. Test
failures may shrink the expected running due to an early termination
or even inflate the running time (\eg, test waiting indefinitely for
an unavailable resources). To mitigate this threat, we filtered
projects with at least 90\% of the tests passing. Only 17\% of our
subjects have failing tests. We carefully inspected our rawdata to
ensure that there is no failing test inflating our results.}
\textit{Internal Validity:} Our results could be influenced by
unintentional mistakes made by humans who interpreted survey data and
implemented scripts and code to collect and analyze data.
For example, we developed JUnit runners to reproduce Maven's parallel
configurations and implemented several scripts to automate our
experiments (\eg, run tests and detect parallelism enabled by default
in the subjects).
All those tasks could introduce bias in our results.
To mitigate those threats, we worked in pairs as to increase chances
of capturing unintentional mistakes.
\textit{Construct Validity:} We considered a number of metrics in this
study that could influence some of our interpretations.  For example,
we measured number of test cases per suite, distribution of test costs
in a suite, time to run a suite, etc.  In principle, these metrics may
not reflect the main problems associated with test
efficiency.
